%-------------------------
% Resume in Latex
% Author: Gourav Barnwal
% Based off of: https://github.com/jakeryang/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
    \uline{\phantom{#1}}%
    \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{5pt}

\titleformat{\section}{
    \vspace{2pt} \scshape \raggedright\large % header section
}{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% sans serif sections
\titleformat{\section}{
    \bfseries \vspace{-7pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-5pt}]

% TODO EBSERIES
% default leftmargin 0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubHeadingListStartForSkills}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEndForSkills}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\color{text-grey}

% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-1pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
    {#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingForSkills}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADING----------
\begin{center}
\textbf{\Huge Gourav Barnwal} \\ \vspace{5pt}
\small \faPhone* \texttt{+91-8250700654} \hspace{1pt} $|$
\hspace{1pt} \faEnvelope \hspace{2pt} \texttt{softenggourav@gmail.com} \hspace{1pt} $|$
\hspace{1pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/softenggourav/}{in/softenggourav/} $|$
\hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/softenggourav}{softenggourav/} $|$
\hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{India}
\\ \vspace{-3pt}
\end{center}
%-----------SUMMARY-----------
\section{SUMMARY}
\resumeSubHeadingListStart
\resumeItem{Senior Software engineer with around 4 years of experience specializing in developing customer-focused, scalable code.}
\resumeSubHeadingListEnd
%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart
\resumeSubheading
{Trinet-Zenefits India - A Digital HR platform for Enterprises}{Dec. 2021 -- Ongoing}
{Senior Software Engineer}{Remote}
\resumeItemListStart
\resumeItem{Played a key role in onboarding and mentoring new team members, guiding them through technical workflows and offering ongoing support.}
\resumeItem{Initiated the implementation of automation process in the fulfillment flow. This enhancement resulted in a remarkable decrease in operation team involvement, reducing involvement from 10k per year to single-digit cases per customer.}
\resumeItem{Led collaboration efforts with external Insurance provider, Principal and Guardian. Develop and implement a backend intensive fulfilment lifecycle, utilizing several REST APIs for all the coverage related data flow.}
\resumeItem{Effectively led the migration of a back-end monolith service from Python 2 to Python 3, ensuring a seamless transition and ongoing integration, leading to improved system maintainability.}
\resumeItem{Managed multiple fulfilment channels like EDI, APIs, Manual form processes for various Insurance provider.}
\resumeItem{Developed and automated reconciliation flow to streamline the efficient sharing and updating of data between brokers and carriers, particularly when employees undergo changes in their insurance plans.}
\resumeItemListEnd
\resumeSubheading
{MoneyTap - A Credit-led Neobank}{Jun. 2020 -- Nov. 2021}
{Software Engineer}{Bangalore, India}
\resumeItemListStart
\resumeItem{Developed a microservice to automate the data collection process in collaboration with an external agency (Karza) for high-value loan customers (loans exceeding INR 5 lakhs), leading to a substantial boost in revenue and customer acquisition.}
\resumeItem{Implemented a comprehensive module to automate the loan collection and legal processes through an external agency (Credgenics), facilitating the recovery of loans from thousands of customers and achieving a monthly loan collection of approximately INR 15 million.}
\resumeItem{Designed and implemented APIs and back-end services enabling customers to trigger loan restructuring options in compliance with RBI guidelines. This initiative resulted in increased revenue and a noteworthy 10\% enhancement in customer lifetime value.}
\resumeItem{Effectively managed and integrated various APIs from lending partner Incred, contributing to reduced loan processing times and enhanced operational efficiency.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------INTERNSHIP-----------
\section{INTERNSHIP}
\resumeSubHeadingListStart
\resumeSubheading
{Shunya - A Learning Management Tool for Schools}{Apr. 2020 -- Jun. 2020}
{Software Engineering Intern}{Bangalore, India}
\resumeItemListStart
\resumeItem{Developed the company website using no-code tool, Webflow. Integrated open-source software Jitsi for video calling. Designed, developed and deployed a Java-based back-end database service via AWS EC2.}
\resumeItemListEnd
\resumeSubheading
{TechMahindra - MakersLab, Research Division}{May 2019 -- Jul. 2019}
{Student Scientist Intern}{Pune, India}
\resumeItemListStart
\resumeItem{Worked on a research project focused on detecting adverse events in live stream videos. Used YOLO and Faster-RCNN deep learning models to improve the detection efficiency. Annotated 20k manually collected images using the Open-Source tool LabelImg.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%-----------SKILLS-----------
\section{SKILLS}
\resumeSubHeadingListStartForSkills
\resumeSubSubheadingForSkills
{\textbf{Language and Tools}: Java(Spring-Boot), Python (Django), SQL, GraphQL, REST-API, Elasticsearch, Kafka}{}{}{}{}
\resumeSubSubheadingForSkills
{\textbf{System Design}: OOPS, LLD, HLD, Design Pattern, Microservice, Unit and Integration Testing}{}{}{}{}
\resumeSubHeadingListEndForSkills

%-----------EDUCATION-----------
\section {EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
{Indian Institute of Technology, Bhubaneswar}{Aug. 2016 -- May 2020}
{\textbf{B.Tech}, Relevant Courses: Data Structures and Algorithms, DBMS, Deep Learning}{Bhubaneswar}
\resumeSubHeadingListEnd

\end{document}